New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-05 Manuscript/Manuscript.Rmd
Continue with M&M

We obtained the dataset of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018]. This open access database is a list of predator-prey interactions that describe several highly-resolved food webs, including biological data about the consumer and resource involved in each trophic interaction (i.e. mean mass). Furthermore, it incorporates information on the interaction itself, such as the dimensionality.
This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected 
since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a 
summary network that ignores seasonal changes [@Jacob2011].

## Data set analyses

Text here.

@@

To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012.

>>>>

We obtained the dataset of the Weddell Sea food web from the GlobAL daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of the German Centre for Integrative Biodiversity Research (iDiv) Halle-Jena-Leipzig [@Brose2018]. This open access database is a list of predator-prey interactions that contains several highly-resolved food webs, including biological data about the consumer and resource species involved in each trophic interaction (i.e. mean mass). Furthermore, it incorporates information on the interaction itself, such as the dimensionality.
This marine food web compiles all the food web data available for the high Antarctic Weddell Sea collected 
since 1983, and is one of the most highly-resolved marine food webs documented to date. It's noteworthy that it is a 
summary network that ignores seasonal changes [@Jacob2011].

## Dataset analyses

We studied the food web of the Weddell Sea by: a) estimating the strength of each interaction; b) analysing the properties of the species in a network approach; and c) comparing the stability of the food web after performing extinction simulations.

@@

To estimate the strength of each interaction in the food web, we followed the methodology proposed by @Pawar2012. The minimum data requirements are: body mass of the consumer (predator) and resource (prey), and the interaction dimensionality classified as 2 or 3 dimensions. GATEWAy v.1.0 does provide information on the mean mass for consumers and resources for every interaction, but lacks the dimensionality for 924 interactions. To solve this issue, we used the information about movement type for consumer and resource. Then, we classified the interaction as 2D when both consumer and resource move in 2D (e.g., both are sessile or walking) or if a consumer moves in 3D and a resource in 2D (e.g., swimming consumer and sessile/walking resource). The interaction was classified as 3D when both consumer and resource move in 3D (e.g., both swimming) or if the consumer moves in 2D and resource in 3D (e.g., sessile/walking consumer, swimming resource) [@Pawar2012].

The main equation for estimating the interaction strength IS is [@Pawar2012]:

```{=tex}
\begin{equation}
IS = \alpha x_R \frac{m_R}{m_C}
\end{equation}
```

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource and the consumer, respectively. We obtained the search rate and the resource density from the relationship with the consumer and resource mass, respectively, suggested by @Pawar2012. Such relationship, a linear regression, varies with the interaction dimensionality.

### 2022-08-05 Manuscript/Manuscript.tex
Continue with M&M

We obtained the dataset of the Weddell Sea food web from the GlobAL
daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
the German Centre for Integrative Biodiversity Research (iDiv)
Halle-Jena-Leipzig \citep{Brose2018}. This open access database is a
list of predator-prey interactions that describe several highly-resolved
food webs, including biological data about the consumer and resource
involved in each trophic interaction (i.e.~mean mass). Furthermore, it
incorporates information on the interaction itself, such as the
dimensionality. This marine food web compiles all the food web data
available for the high Antarctic Weddell Sea collected since 1983, and
is one of the most highly-resolved marine food webs documented to date.
It's noteworthy that it is a summary network that ignores seasonal
changes \citep{Jacob2011}.

\subsection{Data set analyses}

Text here.

@@

To estimate the strength of each interaction in the food web, we
followed the methodology proposed by \citet{Pawar2012}.

>>>>

We obtained the dataset of the Weddell Sea food web from the GlobAL
daTabasE of traits and food Web Architecture (GATEWAy, version 1.0) of
the German Centre for Integrative Biodiversity Research (iDiv)
Halle-Jena-Leipzig \citep{Brose2018}. This open access database is a
list of predator-prey interactions that contains several highly-resolved
food webs, including biological data about the consumer and resource
species involved in each trophic interaction (i.e.~mean mass).
Furthermore, it incorporates information on the interaction itself, such
as the dimensionality. This marine food web compiles all the food web
data available for the high Antarctic Weddell Sea collected since 1983,
and is one of the most highly-resolved marine food webs documented to
date. It's noteworthy that it is a summary network that ignores seasonal
changes \citep{Jacob2011}.

\subsection{Dataset analyses}

We studied the food web of the Weddell Sea by: a) estimating the
strength of each interaction; b) analysing the properties of the species
in a network approach; and c) comparing the stability of the food web
after performing extinction simulations.

@@

To estimate the strength of each interaction in the food web, we
followed the methodology proposed by \citet{Pawar2012}. The minimum data
requirements are: body mass of the consumer (predator) and resource
(prey), and the interaction dimensionality classified as 2 or 3
dimensions. GATEWAy v.1.0 does provide information on the mean mass for
consumers and resources for every interaction, but lacks the
dimensionality for 924 interactions. To solve this issue, we used the
information about movement type for consumer and resource. Then, we
classified the interaction as 2D when both consumer and resource move in
2D (e.g., both are sessile or walking) or if a consumer moves in 3D and
a resource in 2D (e.g., swimming consumer and sessile/walking resource).
The interaction was classified as 3D when both consumer and resource
move in 3D (e.g., both swimming) or if the consumer moves in 2D and
resource in 3D (e.g., sessile/walking consumer, swimming resource)
\citep{Pawar2012}.

The main equation for estimating the interaction strength IS is
\citep{Pawar2012}:

\begin{equation}
IS = \alpha x_R \frac{m_R}{m_C}
\end{equation}

where \vec{\alpha} is the search rate, \vec{x_R} is the density of the
resource, and \vec{m_R} and \vec{m_C} are the body mass of the resource
and the consumer, respectively. We obtained the search rate and the
resource density from the relationship with the consumer and resource
mass, respectively, suggested by \citet{Pawar2012}. Such relationship, a
linear regression, varies with the interaction dimensionality.
